Dancing on Water: The Choreography of Sulfur Dioxide Adsorption to Aqueous Surfaces

### 2011-06-30 Article.tex
New title and abstract as written by Geri

\title{Sulfur Dioxide at Water's Surface}
\author{Eric S. Shamay \and Kevin E. Johnson \and Geraldine L. Richmond}

\begin{document}
\newcommand{\suldiox}{SO$_2$}
\newcommand{\ang}{\,$\textrm{\AA}$}
\newcommand{\angs}{\ang}
\newcommand{\wat}{H$_2$O}

\maketitle

\onehalfspacing

\begin{abstract}
	...Abstract goes here...
\end{abstract}

\include{Introduction}
\include{Background}
\include{Methods}
\include{SteeredMDResults}
\include{EquilibratedResults}

>>>>

\title{Dancing on Water: The Choreography of Sulfur Dioxide Adsorption to Aqueous Surfaces}
\author{Eric S. Shamay \and Kevin E. Johnson \and Geraldine L. Richmond}

\begin{document}

\newcommand{\suldiox}{SO$_2$}
\newcommand{\ang}{\,$\textrm{\AA}$}
\newcommand{\angs}{\ang}
\newcommand{\wat}{H$_2$O}

%\maketitle

%\onehalfspacing
\linenumbers 
\doublespacing

\begin{abstract}
One might expect that the high surface tension of water to be a barrier to adsorption of a gas into the liquid phase, but we know that gaseous adsorption on and into a water surface is a common phenomenon on this planet.  What is not commonly known is how this happens and the interplay between an atmospheric gas such as SO2 and molecules at the water surface that can overcome the barrier created by the strong water-water surface bonding interactions.  What this interplay looks like, the distances from the water surface at which these attractive interactions begin and how they influence the orientational nature of both SO2 and surface water molecules is the focus of this computational study.  The results fill a void in the information about this system existing from previous experimental studies by providing information about the dimensional nature the gas-surface interactions and the details of how the two species twist and turn orientationally with increased surface interactions.  Classical molecular dynamics simulations have been employed in these equilibrium and steered molecular dynamics simulations for SO2 at a neat water surface and at a surface with high interfacial SO2 concentrations.   The results provide new molecular insights for understanding the interaction of this prevalent gas on aerosol and other aqueous surfaces in the environment.
\end{abstract}

\include{Introduction}
\include{Methods}
\include{Results}
\include{Conclusions}

\bibliography{bib/SulfurDioxideText}
